```{r}
source('R/spec_tools.R')
source('R/tofReader.R')
source('R/massCalTools.R')
library(dtw)
library(dplyr)
```

```{r}
# load the data
tof.h5 <- 'testdata/Ac just breath after C (2014-10-23T11h34m53_#).h5'
fid <-H5Fopen(tof.h5)
tofblock <- get.raw.tofblock(fid)
indexhelp <- tof.indexhelp(tofblock)
spec0 <- read.spec.ind(tofblock, indexhelp, 1)
spec1 <- read.spec.ind(tofblock, indexhelp, 700)
spec2 <- read.spec.ind(tofblock, indexhelp, 800)
spec3 <- read.spec.ind(tofblock, indexhelp, 900)
spec4 <- read.spec.ind(tofblock, indexhelp, 901)

inds <- seq_len(indexhelp$N) 
aspec <- function(n) read.spec.ind(tofblock, indexhelp, n)
#rf <- function(x,n) x + aspec(n)
#ss <- Reduce(rf, inds, 0, accumulate=F)
ss <- read.sum.spec(fid)
```

```{r, fig.cap="sum spectrum"}
plot(ss, type='l')
```

```{r}
m2 <- masscal_legacy_smooth(fid, indexhelp)

calib <- m2[1,]
spec <- aspec(1)
ma <- with(calib, (seq_along(spec)-b)^2/a^2)
plot(ma, spec, type='l')

masscal_c1 <- function(fid, indexhelp, 
					   resolution=1e4,
					   mass.low=10,
					   mass.high=200){
  mass_axis <- make_mass_axis(resolution=resolution, mass.low=mass.low, mass.high=mass.high)
}


```{r, fig.cap="original mass calibration jumps"}
# mass calibration jumps
legacy_masscal <- read.mass.cals(fid)
par(mfrow=c(2,1))
plot(legacy_masscal[1,], type='l')
plot(legacy_masscal[2,], type='l')
```

```{r, fig.cap="some smoothing may globally be more effective"}
# mass calibration a smooth one makes maybe sense
df <- as_data_frame(t(legacy_masscal)) %>% mutate(write = 1:nrow(.))
a_smooth <- with(df, smooth.spline(write, V1))
b_smooth <- with(df, smooth.spline(write, V2))

r <- with(indexhelp, 1/dims[[3]])
ci <- indexhelp$calc.indices %>% 
  mutate(x = write - 0.5 + r*buf,
  		 a = predict(a_smooth, x=x)$y,
  		 b = predict(b_smooth, x=x)$y
  		 )

par(mfrow=c(2,1))

plot(df$write, df$V1, type='p')
lines(ci$x, ci$a, col='red', lwd=3)

plot(df$write, df$V2, type='p')
lines(ci$x, ci$b, col='red', lwd=3)
```

## try comparing the results

```{r}
peak_stat <- function(spec0, maxis){
  spec0[1]<-0
  mom0 = sum(spec0)
  mom1 = sum(spec0*maxis)
  mom2 = sum(spec0*maxis^2)
  mm = max(spec0)
  im <- which.max(spec0)
  ig = spec0 > (mm/2)
  tmp <- maxis[ig]
  fwhm <- tmp[length(tmp)]-tmp[1]

  list(mean = mom1/mom0,
	  var = mom2/mom0 - (mom1/mom0)^2,
	  fwhm = fwhm,
	  max.mass = maxis[im])
}

```
### m/z 31

#### only one mass calibration per measurement
```{r}
base.mass <- 31
curr.mass.range <- 
  make_mass_axis( mass.low=base.mass-0.05, 
				  mass.high=base.mass + 0.05)

cal0 <- with(df, list(a=median(V1), b=median(V2)))
spec0 <- spec2mav(ss,cal0, curr.mass.range)

r0 <- peak_stat(spec0, curr.mass.range)
#plot(curr.mass.range, spec0, type='l')
```

```{r, fig.cap="Acetone with only one calibration for whole measurement"}
plot(curr.mass.range, spec0, type='l')
```

#### Tof daq calibration

```{r}
legacy_masscal <- read.mass.cals(fid)

ihc <- indexhelp$calc.indices %>% left_join(df, by='write')

n <- 100
n2spec <- function(ihc,n){
  sa <- aspec(n)
  cala <- with(ihc[n,], list( a=V1, b=V2))
  speca <- spec2mav(sa,cala, curr.mass.range)
}

rfun <- function(x, n){
  x + n2spec(ihc,n)
}

allSpec <- Reduce(rfun, seq_len(indexhelp$N), 0)

plot(curr.mass.range, allSpec, type='l')
#ra <- peak_stat(allSpec, curr.mass.range)
```


#### smooth tof daq

```{r}
legacy_masscal <- read.mass.cals(fid)
df <- as_data_frame(t(legacy_masscal)) %>% mutate(write = 1:nrow(.))
a_smooth <- with(df, smooth.spline(write, V1))
b_smooth <- with(df, smooth.spline(write, V2))

r <- with(indexhelp, 1/dims[[3]])
ci <- indexhelp$calc.indices %>% 
  mutate(x = write - 0.5 + r*buf,
  		 a = predict(a_smooth, x=x)$y,
  		 b = predict(b_smooth, x=x)$y
  		 )

calfun <- function(n)
  ci[n,]

n2spec <- function(cf,n){
  sa <- aspec(n)
  cala <- cf(n)
  speca <- spec2mav(sa,cala, curr.mass.range)
}

rfun <- function(x, n){
  x + n2spec(calfun,n)
}

allSpecS <- Reduce(rfun, seq_len(indexhelp$N), 0)

plot(curr.mass.range, allSpecS, type='l')
rS <- peak_stat(allSpecS, curr.mass.range)
```


```{r, fig.cap="overlay tof daq calibrations"}
plot(curr.mass.range, spec0, type='l')
lines(curr.mass.range, allSpec, col='red')
lines(curr.mass.range, allSpecS, col='blue')
```


## realigning

```{r}
n<- 1000
cumspec <- read.sum.spec(fid)
sa <- aspec(n)
ca <- cumspec-sa

css <- cumsum(sa)
cca <- cumsum(ca)

inds <- seq_along(cca)
af <- approxfun(inds, css, rule=2)


scaled <- function(af,inds,d,e) {
  i2 <- inds/d-e
  c(0,diff(af(i2)))
}


dist_fun <- function(af, d, e){
  sas <- scaled(af,inds, d,e)
  1 - cor(sas,ca)
}

best_shift <-
  optim(c(1,0), 
	  function(x) dist_fun(af, x[[1]], x[[2]])
	  )

es <- seq(-0,0.7,length.out=50)
ed <- sapply(es, function(x) dist_fun(af,best_shift$par[[1]],x))

ds <- seq(1- 2e-5,1.00002,length.out=50)
dd <- sapply(ds, function(x) dist_fun(af,x,best_shift$par[[2]]))

par(mfrow=c(2,1))
plot(es,ed, type='l')
plot(ds,dd, type='l')

```


```{r}
optim_shift <- function(n){
  curr.spec <- aspec(n)
  other.specs <- cumspec-sa
  cum.cur.spec <- cumsum(sa)
  
  work.indices <- seq_along(cumspec)
  inds <- seq_along(curr.spec)
  interp.spec <- approxfun(inds, css, rule=2)
  shifted.spec <- function(x) {
  	e <- x[[1]]
  	d <- x[[2]]
    i2 <- inds/d-e
    c(0,diff(interp.spec(i2)))
  }

  dist2other <- function(x){
	sas <- shifted.spec(x)
	1 - cor(sas, other.specs)
  }

  spec.opt <- optim(c(0,1), dist2other) 
}

optim_shift(4)

```
